SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-26 docs/questioning.tex
clarifications on related work and covered area in section 1

In our research we focus on the top
{\sc tba} systems that counter application attacks, in terms of
citations.
% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.

@@

Here we analyze the three different protection approaches.

>>>>

There is already a survey on mitigating
software vulnerabilities in general~\cite{SZ12}.
The scope of that research is pretty wide and leaves
out many approaches and mechanisms that we report here.
This is mainly because this work includes countermeasures
that detect such vulnerabilities via program analysis
(which is done during development or testing), while
we include protection mechanisms that counter
such attacks when they take place.
Also, countermeasures that prevent {\sc sql}
injection attacks~\cite{HVO06}, have already been surveyed.
However, this survey is quite old and since then
the number of countermeasures that detect {\sc sql}
injection attacks alone, has been drastically increased
as we mentioned in the previous paragraph.
In our research we focus on the top
{\sc tba} systems that counter application attacks, in terms of
citations.

% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.

@@

Here we analyze the {\sc tba} different protection approaches.
